The state learner -- a super learner for right-censored data

### 2024-05-27 tex/journal-version/manuscript.tex
nicely shortened intro

Medical decision making is traditionally based on the discrepancy
between intuitive judgment and the law of chance
\citep{redelmeier1995probability}. We are concerned with the
statistical models that provide probabilistic predictions about the
medical future of a patient. We have two different applications of
these models in mind. One is as a stand-alone tool where the model
provides predictions about the future, such as the predicted risk of
adverse outcomes for a newly diagnosed patient. The other is as input
to an algorithm which estimates a causal target parameter such as an
average treatment effect and depends on estimates of nuisance
parameters such as the conditional probability of being uncensored.
An example of the latter is the targeted minimum loss based estimator
\citep{rytgaard2022targeted}. In both applications, the models have to
be learned based on available data from previous patients.

A super learner is a machine learning algorithm that combines a finite
set of learners into a meta learner by estimating prediction
performance in hold-out samples using a pre-specified loss function
\citep{van2007super}. When the aim is to make a prediction model,
super learners combine strong learners, such as Cox regression models
and random survival forests \citep[][Section 8.4]{gerds2021medical}.
% For targeted learning of a low dimensional
% target parameter in presence of a high-dimensional nuisance parameter,
% a super learner will usually also include the highly adaptive lasso
% \citep{van2011targeted, benkeser2016highly,van2017generally}.
While the general idea of combining strong learners based on cross-validation
stems from earlier work \citep{wolpert1992stacked,breiman1996stacked}, the
name super learner is justified by an oracle inequality
\citep{van2003unicv,vaart2006oracle}.
% The super learner is guaranteed to perform
% almost as well as the model which minimises the expected performance, i.e., the
% model we would select if we could evaluate the prediction performance in an
% infinite hold-out sample.
The work presented in this article is motivated by the choice of the
loss function for super learning in survival analysis. Existing super
learner algorithms for right-censored data use partial log-likelihood
loss or inverse probability of censoring weighted loss
\citep{polley2011-sl-cens,keles2004asymptotically,golmakani2020super,gonzalez2021stacked,westling2021inference}.
Unfortunately, the use of the partial log-likelihood loss restricts
the class of learners and excludes for example simple Kaplan-Meier
based learners and also more complex random survival forest
algorithms. For this reason \cite{golmakani2020super} restrict their
learners to Cox proportional hazard models. A lesser known fact is
that a super learner constructed with the negative partial
log-likelihood loss implicitly depends on the censoring distribution
\citep{hjort1992inference,whitney2019comment}. Inverse probability of
censoring weighted loss has been studied for decades
\citep{graf1999assessment, hothorn2006survival,
  gerds2006consistent}. A disadvantage of inverse probability of
censoring weighted loss estimators is that they require a
pre-specified model for the censoring distribution. Recently
\cite{westling2021inference} proposed a procedure which iterates
between super learning of the censoring distribution and super
learning of the event time distribution. In this article, we pursue a
different route.

We define the state learner, a new super learner for right-censored
data, which simultaneously estimates the expected loss of learners of
the event time distribution and the censoring distribution. The loss
function underlying the state learner operates on the coarsened
data. In the right censored survival setting the coarsened data
consist of the minimum and the order of the censoring time and the
event time as well as the baseline covariates. The state learner can
include a broad class of survival models as learners, it can handle
competing risks, and it does not require a single pre-specified
estimator of the conditional censoring distribution. To analyze the
theoretical properties of the state learner we focus on the discrete
super learner which combines the library of learners by picking the
one that minimises the cross-validated loss \citep{van2007super}. In
the presence of competing risks, our algorithm uses separate libraries
of learners for the cumulative hazard functions for each of the
competing risks and for the censoring distribution. We show that the
oracle selector of the state learner is consistent if all libraries
contain a consistent learner and prove a finite sample oracle
inequality. The result of the state learner algorithm could be a
medical risk prediction model \citep{gerds2021medical} which predicts
the probability of an event based on covariates in the presence of
competing risks. The other application is in targeted learning where
conditional event probabilities occur as high-dimensional nuisance
parameters which need to be estimated at a certain rate
\citep{van2011targeted, rytgaard2021estimation, rytgaard2022targeted}.
For the asymptotic bias term of targeted estimator, which uses the
state learner to estimate nuisance parameters, we show that a second
order product structure holds. We illustrate both applications of the
state learner with prostate cancer data
\citep{kattan2000pretreatment}.

\subsection{Existing methods}
\label{sec:relat-liter-exist}

Machine learning based on right-censored data commonly uses the
negative partial log-likelihood as a loss function
\citep[e.g.,][]{li2016regularized,yao2017deep,lee2018deephit,katzman2018deepsurv,gensheimer2019scalable,lee2021boosted,kvamme2021continuous}.
This loss function is however not perfectly suited for super learning
because it cannot be applied to prominent survival learners. For
example, the Kaplan-Meier estimator, the random survival forest, and
the semi-parametric Cox regression model provide cumulative hazard
functions that are piece-wise constant in the time argument. Suppose
these methods were applied to a learning data set and the aim is to
evaluate the partial log-likelihood loss in an independent test data
set. Suppose further that the test data set contains event times that
were not also seen in the learning data set, as it would naturally
happen when the events are observed in continuous time. The problem is
that these methods assign zero probability to all the event times in
the test set which were not also contained in the training data set.
Hence the partial log-likelihood loss in the test set would be
infinity (the logarithm of zero is infinity).

When a proportional hazards model is assumed, the baseline hazard
function can be profiled out of the likelihood \citep{cox1972regression}.
The cross-validated partial log-likelihood loss  \citep{verweij1993cross} has therefore been
suggested as a loss function for super learning which however
restricts the library of learners to include only Cox proportional
hazards models \citep{golmakani2020super}.

Another approach for super learning with right-censored data is to use an
inverse probability of censoring weighted (IPCW) loss function
\citep{graf1999assessment,van2003unicv,molinaro2004tree,keles2004asymptotically,hothorn2006survival,gerds2006consistent,gonzalez2021stacked}.
An IPCW loss function is attractive because the associated risk does not depend
on the censoring distribution but describes a feature of the population of
interested. Similar results can be obtained using censoring unbiased
transformations \citep{fan1996local,steingrimsson2019censoring} or pseudo-values
\citep{andersen2003generalised,mogensen2013random,sachs2019ensemble}. All these
methods rely on an estimator of the censoring distribution, and their drawback
is that this estimator has to be pre-specified. When the data-generating
mechanism is complex and not well-understood, pre-specification of the censoring
distribution is a challenge.

An attempt to avoid a pre-specified censoring model was proposed independently
by \cite{han2021inverse} and \cite{westling2021inference}. In both articles, the
authors suggest to iterate between learning of the outcome model and learning of
the censoring model using IPCW loss functions. However, no general theoretical
guarantees seem to exist for this procedure, and it has not yet been extended to
the situation with competing risks.

\subsection{Organization of article}

We introduce our notation and framework in
Section~\ref{sec:framework}. In Section~\ref{sec:super-learning} we
define general super learning for right-censored data.
% , and in
% Section~\ref{sec:relat-liter-exist} we review existing methods.
Section~\ref{sec:super-learner-simple} introduces the state learner,
and Section~\ref{sec:theor-results-prop} provides theoretical
guarantees. In Section~\ref{sec:targeted-learning} we discuss the use
of the state learner in the context of targeted learning. We report
results of our numerical experiments in Section~\ref{sec:numer-exper}
and analyze a prostate cancer data set in
Section~\ref{sec:real-data-appl}.  Section~\ref{sec:discussion}
contains a discussion of the merits and limitations of our
proposal. Appendices~\ref{sec:proof-proposition}
and~\ref{sec:state-learner-with} contain proofs.
An implementation of the state learner is available at
\url{https://github.com/amnudn/statelearner} along with codes for reproducing
our numerical experiments.

@@

% The problem with most existing super learners for right-censored data is that
% they depend on a pre-specified estimator of the censoring distribution.
The main idea of the state learner is to jointly use learners for
\( \Lambda_1 \), \( \Lambda_2 \), and \( \Gamma \), and the relations in
equation~(\ref{eq:parametrizeP}), to learn a feature of the observed data
distribution \( P \). The discrete state learner ranks a tuple of learners for
the tuple of the cumulative hazard functions
\( (\Lambda_1, \Lambda_2, \Gamma) \) based on how well they jointly model the
observed data. Risk predictions can then be obtained by combining
\( \Lambda_1 \) and $\Lambda_2$ from the highest ranked tuple using a well-known
formula \citep{benichou1990estimates, ozenne2017riskregression}. To formally
introduce the state learner, we define the multi-state process
\begin{equation*}
  \eta(t) = \1\{\tilde{T} \leq t, \tilde D=1\} + 2\,\1\{\tilde{T} \leq t, \tilde
  D=2\} - \1\{\tilde{T} \leq t, \tilde D=0\},
  \quad \text{for} \quad t \in [0, \tau].
\end{equation*}
At time \(t\), we observe that each individual is in one of four mutually
exclusive states (Figure \ref{fig:multi-state-process}).

\begin{figure}[h]
  \centering %
  \includeFigCond[width=.5\textwidth]{figure-multi-state-process.pdf}
  \caption{Illustration of the multi-state process \(\eta\) used by
    the state learner. Note that `censored' is a state, hence the
    process is always observed at any time.}
  \label{fig:multi-state-process}
\end{figure}

@@

In this section we use the prostate cancer data of
\cite{kattan2000pretreatment} to illustrate the use of the state
learner in the presence of competing risks. We have introduced the
data in Section~\ref{sec:numer-exper}. The data consists of 1,042
patients who are followed from start of followup until tumor
recurrence, death without tumor recurrence or end of followup
(censored) whatever came first. For the sole purpose of illustration,
we estimate the average treatment effect of hormone therapy on death
and tumor recurrence. To do this we adapt the estimation strategy of
Section~\ref{sec:targeted-learning} as follows.  We use the state
learner to rank libraries of learners for the cause-specific
cumulative hazard functions of tumor recurrence, death without tumor
recurrence, and censoring.  The libraries of learners include the five
learners described in Table~\ref{tab:zel-library}.  We use the same
set of learners to learn the cumulative hazard function of tumor
recurrence \( \Lambda_1 \), the cumulative hazard function of death
without tumor recurrence \( \Lambda_2 \), and the cumulative hazard
function of the conditional censoring distribution $\Gamma$. 
We then use the highest ranked combination
of learners and apply formula~\eqref{eq:one-step-comp-ate}.

\begin{table}
  \caption{\label{tab:zel-library}Overview of the five learners used by the
    state learner when applied to the prostate cancer data set. The Kaplan-Meier
    estimator was fitted using the package \texttt{prodlim}
    \citep{Gerds_2019prodlim}. All Cox models included all five covariates in
    the model and were fitted using the package \texttt{survival}
    \citep{survival-package}. All penalised Cox models included all five
    covariates as linear predictors and were fitted using the package
    \texttt{glmnet} \citep{glmnet-cox,glmnet-glm}. The random forest was fitted
    with the package \texttt{randomForestSRC} \citep{rfsrc-paclage}.}
  \centering
  \begin{tabular}{lll}
    \toprule
    Family & Model & Description \\
    \midrule
    Marginal & \texttt{KM} & The Kaplan-Meier estimator \\ 
    Cox & \texttt{Cox} & All five covariates included with additive effects \\
           & \( \texttt{Cox strata CS} \)  & Cox model stratified on CS  \\
           % & \( \texttt{Cox strata HT} \)  & Cox model stratified on HT \\
           % & \( \texttt{Cox spline} \)  & PSA and RD modeled with splines \\ 
    Penalised Cox & \texttt{Lasso} & Cox model with \( L_1 \)-norm penalty   \\
           % & \texttt{Ridge} & Cox model with \( L_2 \)-norm penalty \\
           & \texttt{Elastic} & Cox model with \( L_1 \)- and \( L_2 \)-norm penalty \\
    Random forest & \texttt{RF} & Random forest with default settings \\
    \bottomrule 
  \end{tabular}
\end{table}

This gives a library consisting of \( 5^3 = 125 \) learners for the conditional
state occupation probability function \( F \) defined in
equation~(\ref{eq:F-def}). We use five folds for training and testing the
models, and we repeat training and evaluation five times with different splits.
The integrated Brier score (defined in Section~\ref{sec:super-learner-simple})
for all learners are shown in Figure~\ref{fig:zelefski-real}, and the top 10
combinations of learners are displayed in Table~\ref{tab:zelefski-real}. We see
that the prediction performance is mostly affected by the choice of learner for
the censoring distribution. Several combinations of learners give similar
performance as measured by the integrated Brier score, as long as a random
forest is used to model the censoring distribution.

\begin{figure}
  \centering %
  \includeFigCond[width=.9\linewidth]{real-data-state-learner.pdf}
  \caption[]{The results of applying the 125 combinations of learners to the
    prostate cancer data set. The learners are \texttt{KM} (KM), \texttt{Cox
      strata CS} (strata), \texttt{Lasso} (lasso), \texttt{Elastic} (elastic),
    and \texttt{RF} (RF) as described Table~\ref{tab:zel-library}. The error
    bars are based on five repetitions using different splits. We refer to
    learners of \( \Lambda_1 \), \( \Lambda_2 \), and $\Gamma$ as `Tumor
    learner', `Death learner', and `Censoring learner', respectively.}
  \label{fig:zelefski-real}
\end{figure}

\begin{table}
  \caption{\label{tab:zelefski-real}The 10 best performing models in terms of integrated Brier score. The
    reported standard errors are based on five repetitions using different
    splits. The models are described in Table~\ref{tab:zel-library}. We refer to
    learners of \( \Lambda_1 \), \( \Lambda_2 \), and $\Gamma$ as `Tumor
    learner', `Death learner', and `Censoring learner', respectively.}
  \centering
  \input{./real-data-tab.tex}
\end{table}

>>>>

% Medical decision making is traditionally based on the discrepancy
% between intuitive judgment and the law of chance
% \citep{redelmeier1995probability}.
% We are concerned with the statistical models that provide
% probabilistic predictions about the medical future of a patient. We
% have two different applications of these models in mind. One is as a
% stand-alone tool which predicts the likelihood of medical outcomes.
% The other is as nuisance parameter estimate
% input to an algorithm which estimates a causal target
% parameter such as an average treatment effect and depends on estimates
% of nuisance parameters such as the conditional probability of being
% uncensored.  An example of the latter is the targeted minimum loss
% based estimator \citep{rytgaard2022targeted}. In both applications,
% the models have to be learned based on available data from previous
% patients.
A super learner is a machine learning algorithm that combines a finite
set of learners into a meta learner by estimating prediction
performance in hold-out samples using a pre-specified loss function
\citep{van2007super}. When the aim is to make a prediction model,
super learners combine strong learners, such as Cox regression models
and random survival forests \citep[][Section 8.4]{gerds2021medical}.
% For targeted learning of a low dimensional
% target parameter in presence of a high-dimensional nuisance parameter,
% a super learner will usually also include the highly adaptive lasso
% \citep{van2011targeted, benkeser2016highly,van2017generally}.
While the general idea of combining strong learners based on cross-validation
stems from earlier work \citep{wolpert1992stacked,breiman1996stacked}, the
name super learner is justified by an oracle inequality
\citep{van2003unicv,vaart2006oracle}.
% The super learner is guaranteed to perform
% almost as well as the model which minimises the expected performance, i.e., the
% model we would select if we could evaluate the prediction performance in an
% infinite hold-out sample.

We define the state learner, a new super learner for right-censored
data, which simultaneously estimates the expected loss of learners of
the event time distribution and the censoring distribution. The loss
function underlying the state learner operates on the coarsened
data. In the right censored survival setting the coarsened data
consist of the minimum and the order of the censoring time and the
event time as well as the baseline covariates. The state learner can
include a broad class of survival models as learners, it can handle
competing risks, and it does not require a single pre-specified
estimator of the conditional censoring distribution. To analyze the
theoretical properties of the state learner we focus on the discrete
super learner which combines the library of learners by picking the
one that minimises the cross-validated loss \citep{van2007super}. In
the presence of competing risks, our algorithm uses separate libraries
of learners for the cumulative hazard functions for each of the
competing risks and for the censoring distribution. We show that the
oracle selector of the state learner is consistent if all libraries
contain a consistent learner and prove a finite sample oracle
inequality.

Machine learning based on right-censored data commonly uses the
partial log-likelihood as a loss function
\citep[e.g.,][]{li2016regularized,yao2017deep,lee2018deephit,katzman2018deepsurv,gensheimer2019scalable,lee2021boosted,kvamme2021continuous}.
However, this loss function does not work well with data splitting
(cross-validation) because the partial log-likelihood loss assigns an
infinite value when applied to a test set time point which does not
occur in the learning set as soon as the learner predicts piece-wise
constant cumulative hazard functions. This is the case for prominent
survival learners including the Kaplan-Meier estimator, the random
survival forest, and the semi-parametric Cox regression model.  When a
proportional hazards model is assumed, the baseline hazard function
can be profiled out of the likelihood \citep{cox1972regression}.  The
cross-validated partial log-likelihood loss \citep{verweij1993cross}
has therefore been suggested as a loss function for super learning
which however restricts the library of learners to include only Cox
proportional hazards models \citep{golmakani2020super}.
% A lesser
% known fact is that a super learner constructed with the partial
% log-likelihood loss implicitly depends on the censoring distribution
% \citep{hjort1992inference,whitney2019comment}.

Alternative approaches for super learning with right-censored data use
an inverse probability of censoring weighted (IPCW) loss function
\citep{graf1999assessment,van2003unicv,molinaro2004tree,keles2004asymptotically,hothorn2006survival,gerds2006consistent,gonzalez2021stacked},
% An IPCW loss function is attractive because the associated risk does
% not depend on the censoring distribution but describes a feature of
% the population of interested. Similar results can be obtained using
censoring unbiased transformations
\citep{fan1996local,steingrimsson2019censoring}, or pseudo-values
\citep{andersen2003generalised,mogensen2013random,sachs2019ensemble}.
All these methods rely on an estimator of the censoring distribution,
and their drawback is that this estimator has to be pre-specified.
% When the data-generating mechanism is complex and not
% well-understood, pre-specification of the censoring distribution is a
% challenge.
% Inverse probability of censoring weighted loss has been studied for
% decades \citep{graf1999assessment, hothorn2006survival,
  % gerds2006consistent}. A disadvantage of inverse probability of
% censoring weighted loss estimators is that they require a
% pre-specified model for the censoring distribution.
% Recently \cite{westling2021inference} proposed a procedure which
% iterates between super learning of the censoring distribution and
% super learning of the event time distribution.
An approach which avoids a pre-specified censoring model was proposed
independently by \cite{han2021inverse} and
\cite{westling2021inference}. In both articles, the authors suggest to
iterate between learning of the outcome model and learning of the
censoring model using IPCW loss functions. However, no general
theoretical guarantees seem to exist for this procedure, and it has
not yet been extended to the situation with competing risks.

The result of the state learner algorithm could be a medical risk
prediction model \citep{gerds2021medical} which predicts the
probability of an event based on covariates in the presence of
competing risks. The other application is in targeted learning where
conditional event probabilities occur as high-dimensional nuisance
parameters which need to be estimated at a certain rate
\citep{van2011targeted, rytgaard2021estimation, rytgaard2022targeted}.
For the asymptotic bias term of targeted estimator, which uses the
state learner to estimate nuisance parameters, we show that a second
order product structure holds. We illustrate both applications of the
state learner with prostate cancer data
\citep{kattan2000pretreatment}. We introduce our notation and
framework in Section~\ref{sec:framework}. In
Section~\ref{sec:super-learning} we define general super learning for
right-censored data. Section~\ref{sec:super-learner-simple} introduces
the state learner, and Section~\ref{sec:theor-results-prop} provides
theoretical guarantees. In Section~\ref{sec:targeted-learning} we
discuss the use of the state learner in the context of targeted
learning. We report results of our numerical experiments in
Section~\ref{sec:numer-exper} and analyze a prostate cancer data set
in Section~\ref{sec:real-data-appl}.  Section~\ref{sec:discussion}
contains a discussion of the merits and limitations of our
proposal. Appendices~\ref{sec:proof-proposition}
and~\ref{sec:state-learner-with} contain proofs.  An implementation of
the state learner is available at
\url{https://github.com/amnudn/statelearner} along with codes for
reproducing our numerical experiments.

@@

% The problem with most existing super learners for right-censored data is that
% they depend on a pre-specified estimator of the censoring distribution.
The main idea of the state learner is to jointly use learners for
\( \Lambda_1 \), \( \Lambda_2 \), and \( \Gamma \), and the relations in
equation~(\ref{eq:parametrizeP}), to learn a feature of the observed data
distribution \( P \). The discrete state learner ranks a tuple of learners for
the tuple of the cumulative hazard functions
\( (\Lambda_1, \Lambda_2, \Gamma) \) based on how well they jointly model the
observed data. Risk predictions can then be obtained by combining
\( \Lambda_1 \) and $\Lambda_2$ from the highest ranked tuple using a well-known
formula \citep{benichou1990estimates, ozenne2017riskregression}. To formally
introduce the state learner, we define the multi-state process
  \eta(t) = \1\{\tilde{T} \leq t, \tilde D=1\} + 2\,\1\{\tilde{T} \leq t, \tilde
  D=2\} - \1\{\tilde{T} \leq t, \tilde D=0\},
  \quad \text{for} \quad t \in [0, \tau].
At time \(t\), we observe that each individual is in one of four mutually
exclusive states. % (Figure \ref{fig:multi-state-process}).
% \begin{figure}[h]
  % \centering %
  % \includeFigCond[width=.5\textwidth]{figure-multi-state-process.pdf}
  % \caption{Illustration of the multi-state process \(\eta\) used by
    % the state learner. Note that `censored' is a state, hence the
    % process is always observed at any time.}
  % \label{fig:multi-state-process}
% \end{figure}

@@

In this section we use the prostate cancer data of
\cite{kattan2000pretreatment} to illustrate the use of the state
learner in the presence of competing risks. We have introduced the
data in Section~\ref{sec:numer-exper}. The data consists of 1,042
patients who are followed from start of followup until tumor
recurrence, death without tumor recurrence or end of followup
(censored) whatever came first. For the sole purpose of illustration,
we estimate the average treatment effect of hormone therapy on death
and tumor recurrence. To do this we adapt the estimation strategy of
Section~\ref{sec:targeted-learning} as follows. We use the state
learner to rank libraries of learners for the cause-specific
cumulative hazard functions of tumor recurrence, death without tumor
recurrence, and censoring.  The libraries of learners each include
five learners: a Nelson-Aalen, three Cox regression models
(unpenalized, Lasso, Elastic net) each including additive effects of
the 5 covariates (Section~\ref{sec:numer-exper}), and a random
survival forest. We use the same set of learners to learn the
cumulative hazard function of tumor recurrence \( \Lambda_1 \), the
cumulative hazard function of death without tumor recurrence
\( \Lambda_2 \), and the cumulative hazard function of the conditional
censoring distribution $\Gamma$.  We then use the highest ranked
combination of learners and apply
formula~\eqref{eq:one-step-comp-ate}.

% \begin{table}
  % \caption{\label{tab:zel-library}Overview of the five learners used by the
    % state learner when applied to the prostate cancer data set. The Kaplan-Meier
    % estimator was fitted using the package \texttt{prodlim}
    % \citep{Gerds_2019prodlim}. All Cox models included all five covariates in
    % the model and were fitted using the package \texttt{survival}
    % \citep{survival-package}. All penalised Cox models included all five
    % covariates as linear predictors and were fitted using the package
    % \texttt{glmnet} \citep{glmnet-cox,glmnet-glm}. The random forest was fitted
    % with the package \texttt{randomForestSRC} \citep{rfsrc-paclage}.}
  % \centering
  % \begin{tabular}{lll}
    % \toprule
    % Family & Model & Description \\
    % \midrule
    % Marginal & \texttt{KM} & The Kaplan-Meier estimator \\ 
    % Cox & \texttt{Cox} & All five covariates included with additive effects \\
           % & \( \texttt{Cox strata CS} \)  & Cox model stratified on CS  \\
    % Penalised Cox & \texttt{Lasso} & Cox model with \( L_1 \)-norm penalty   \\
           % & \texttt{Elastic} & Cox model with \( L_1 \)- and \( L_2 \)-norm penalty \\
    % Random forest & \texttt{RF} & Random forest with default settings \\
    % \bottomrule 
  % \end{tabular}
% \end{table}

This gives a library consisting of \( 5^3 = 125 \) learners for the
conditional state occupation probability function \( F \) defined in
equation~(\ref{eq:F-def}). We use five folds for training and testing
the models, and we repeat training and evaluation five times with
different splits.  The integrated Brier score (defined in
Section~\ref{sec:super-learner-simple}) for all learners are shown in
Figure~\ref{fig:zelefski-real}. We see that the prediction
performance is mostly affected by the choice of learner for the
censoring distribution. Several combinations of learners give similar
performance as measured by the integrated Brier score, as long as a
random forest is used to model the censoring distribution.

\begin{figure}
  \centering %
  \includeFigCond[width=.9\linewidth]{real-data-state-learner.pdf}
  \caption[]{The results of applying the 125 combinations of learners to the
    prostate cancer data set. The learners are \texttt{KM} (KM), \texttt{Cox
      strata CS} (strata), \texttt{Lasso} (lasso), \texttt{Elastic} (elastic),
    and \texttt{RF} (RF) as described Table~\ref{tab:zel-library}. The error
    bars are based on five repetitions using different splits. We refer to
    learners of \( \Lambda_1 \), \( \Lambda_2 \), and $\Gamma$ as `Tumor
    learner', `Mortality learner', and `Censoring learner', respectively.}
  \label{fig:zelefski-real}
\end{figure}

% \begin{table}
  % \caption{\label{tab:zelefski-real}The 10 best performing models in terms of integrated Brier score. The
    % reported standard errors are based on five repetitions using different
    % splits. The models are described in Table~\ref{tab:zel-library}. We refer to
    % learners of \( \Lambda_1 \), \( \Lambda_2 \), and $\Gamma$ as `Tumor
    % learner', `Mortality learner', and `Censoring learner', respectively.}
  % \centering
  % \input{./real-data-tab.tex}
% \end{table}
